A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-23 paper.tex
acknowledgement to crc
small modify

\documentclass{sig-alternate}
\usepackage{url}
\usepackage[flushleft]{threeparttable}
\begin{document}

@@

\begin{itemize}
\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system)~\cite{matthews2009towards}.
\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
\end{itemize}

@@

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
with two top quarks allows to measure the Higgs coupling strength to
top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
itself, it has to be reconstructed from its decay products.

@@

{\bf Data Sources.}
The CMS collaboration provides analysis end-users with a pre-processed
and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
proton-proton collisions with a signature of interest, in the form of
reconstructed particles.  This format is based on the RAW output of
the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms derive signatures of individual particles.
Both real and simulated data are available for examination.

@@

\item {\bf Configuration Complexity.}  As a means of controlling the complexity
of dependent software packages, the high energy physics community has developed
a number of tools that perform run-time configuration and consistency checks
of the available software.  {\tt scram} is the software management tool used
by the CMS experiment.  Before running any code, {\tt scram} is used to locate
the appropriate version software,  set environment variables such as the PATH, run any
tool-specific configuration, and do the same for all software on which it depends.
If the correct versions are not available, {\tt scram} halts and emits an error.
While this procedure has great value for consistency, it also introduces a significant cost
because it involves a large number of nested scripts traversing a filesystem,
repeatedly looking up metadata.  In our example, the time to perform this configuration
with a cold cache is about 14 minutes, which is almost as large as the actual analysis
run, which takes 20 minutes.

@@

\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
program is very large, the size of the data and software actually used are much smaller.
Often, an entire repository or data source is named within the script, but the program
only needs a handful of items from that source.  For example, the data is stored on an
HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
The CMSSW repository is 88.1GB in total
but only 448.3MB in source are checked out, and the software actually used only
measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
whether it is needed or not.

\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
between collecting the initial email, analyzing the program, and writing this
paper, the computing environment was under continuous change.  The CMSSW software
distribution released a new version, the target execution environment was upgraded
to a new operating system, and the application deprecated the use of CVS for obtaining
the software.  While the users of this software seem be accustomed to constant change,
any preservation technique will have to be very cautious about relying upon an
external service, even one that may appear to be highly stable.

@@

It is clear that the artifact, as provided, is not in a suitable form
for preservation.  While it might be technically possible to automatically
capture the entire virtual machine and all of the connected filesystems,
it would require 166.8TB of storage, which would be prohibitively expensive
for capturing this one application is alone.  Further, if multiple
similar applications are preserved, we would miss the opportunity to identify
common dependencies and store them once for multiple artifacts.
A more structured approach to dependency management is needed.

@@

Parrot is a virtual filesystem access tool which has been used to attach
existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
It works by trapping an application's system calls through the {\tt ptrace} debugging
interface, and then replacing them with the desired I/O operations.  Parrot is already used
in the high energy physics community with applications like TauRoast specifically to 
provide access to the CMSSW software distribution via the CVMFS distributed file system.
We made small modifications to Parrot to record a \emph{namelist} which lists all 
of the files that an application actually accesses.

@@

For one execution of \emph{TauRoast}, the namelist 132,047 accessed filenames,
along with the operation used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
With duplicate filenames removed, the list is reduced to 67,168 files.
Many of those entries do not exist, because they reflect attempts
by the application to search for programs and libraries in multiple places.
Only 22,068 entries reflect existing files or directories.

@@

We evaluated the correctness of the reduced package and the overhead of generating the package.
To do this, the application was repeated with the help of Original Script (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
Then one reduced package was generated and verified with the help of Parrot on the original machine.

@@

We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
Then based on the successful execution of Original-Script, Reduced-Package is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.

To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset. We also counted the time used to obtain the filename list and generate the package. To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced-Package.
Original-Script does not support mining of implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Original-Script and Reduced-Package.
Reduced-Package is faster than Original-Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
and all the environment building only takes 4 seconds,
We were surprised that Reduced-Package even reduces the actual analysis time. 
The reason for this is that data is obtained through accessing HDFS in Original-Script, but is copied into the package in Reduced-Package. This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Original& \bf Reduced\\ 
    \bf Category & \bf Script & \bf Package\\ \hline
    Obtain Namelist & N/A & 28min 28s \\ \hline
    Generate Package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 4s \\ \hline
    Analysis Code & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Original-Script and Reduced-Package}
    \label{table:time-2nd3rd}
\end{table}

Table~\ref{table:time-2nd3rd} also illustrates the time used to
obtain the filename list and generate the package. 
The time used for these two steps is longer than the execution time,
because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
However, 
this is only done once.
Once the package is
generated, many users can directly obtain the package and repeat the application 
separately.

Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
The third column corresponds to the data size of Reduced-Package and can be easily figured out, because all the necessary data has been copied into the package.
Original-Script does not support measuring implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

To further verify the correctness of Reduced-Package on other machines, two different machines are employed -
one virtual
machine~\cite{goldberg1974survey} from Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
and one virtual machine from amazon EC2~\cite{amazon2010amazon} based on Xen.

Table~\ref{table:config-vm} illustrates the configuration of 
each machine and the execution time of the application on each machine.
All the machines adopt the x86\_64 hardware platform and Linux OS.
Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
The execution time on one machine greatly depends on its hardware configuration.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|r|}
    \hline
    \bf Machine & \bf Distro & \bf CPU & \bf Mem & \bf Execution\\ 
    \bf Type   &\bf Version&\bf Cores & (\bf GB) & \bf Time\\ \hline
    Native &  Red Hat  & 64 & 125 & 13min 04s\\  
    Machine& 5.10 &&&\\ \hline
    KVM & CentOS & 4 & 2 & 21min 38s\\
    (Notre Dame)&5.10 &&&\\ \hline
    Xen & Red Hat & 16 & 60.5 & 13min 30s\\ 
    (EC2) &5.9 &&&\\ \hline
    \end{tabular}
    \caption{Evaluation of Different Machines}
    \label{table:config-vm}
\end{table}

Regardless, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS distribution version.
%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.

@@

Generally, there are three approaches to preserve software environment:
hardware preservation, migration and emulation.  Hardware
preservation preserves the original software and its original operating
environment. 
Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
However, migration often involves the re-compiling and re-configuring
the source code to accustom a new hardware platform and software environment.
Emulation recreates the original software and hardware environment by
programming future platforms and OSs. One common solution to implement this is
virtual machine. According to the usage and emulation degree of the real
machine, virtual machine can be divided into system virtual machine and process
virtual machine. 
The working principle, design principle and
performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
The
functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
scientific simulations in Java. 
The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.

@@

Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing preserved software library has been made. 
The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
J. R. Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.

@@

B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.

@@

This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
OCI-1148330 (SI2) and PHY-1312842.  We also thank the support and help of the Center for Research Computing (CRC) of University of Notre Dame.

\bibliographystyle{abbrv}
\bibliography{cclpapers,this}

>>>>

\documentclass{sig-alternate}
\usepackage{url}
\usepackage[flushleft]{threeparttable}
\hyphenation{resour-ces}
\hyphenation{approac-hes}
\hyphenation{har-der}
\hyphenation{spe-cifically}
\begin{document}

@@

\begin{itemize}
\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
\end{itemize}

@@

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
with two top quarks allows measuring the Higgs coupling strength to
top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
itself, it has to be reconstructed from its decay products.

@@

{\bf Data Sources.}
The CMS collaboration provides end-users with a pre-processed
and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
proton-proton collisions with a signature of interest, in the form of
reconstructed particles.  This format is based on the RAW output of
the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
Both real and simulated data are available for examination.

@@

\item {\bf Configuration Complexity.}  As a means of controlling the complexity
of dependent software packages, the high energy physics community has developed
a number of tools that perform run-time configuration and consistency checks
of the available software.  {\tt scram} is the software management tool used
by the CMS experiment.  Before running any code, {\tt scram} is used to locate
the appropriate version of software,  set environment variables such as the PATH, run any
tool-specific configuration, and do the same for all software on which it depends.
If the correct versions are not available, {\tt scram} halts and emits an error.
While this procedure has great value for consistency, it also introduces a significant cost
because it involves a large number of nested scripts traversing a filesystem,
repeatedly looking up metadata.  In our example, the time to perform this configuration
with a cold cache is about 14 minutes, which is almost as large as the actual analysis
run, which takes 20 minutes.

@@

\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
program is very large, the size of the data and software actually used are much smaller.
Often, an entire repository or data source is named within the script, but the program
only needs a handful of items from that source.  For example, the data is stored on an
HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
The CMSSW repository is 88.1GB in total
but only 448.3MB of source is checked out, and the actually used software only
measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
whether it is needed or not.

\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
between collecting the initial email, analyzing the program, and writing this
paper, the computing environment continuously changed.  The CMSSW software
distribution released a new version, the target execution environment was upgraded
to a new operating system, and the application deprecated the use of CVS for obtaining
the software.  While the users of this software seem be accustomed to constant change,
any preservation technique will have to be very cautious about relying upon an
external service, even one that may appear to be highly stable.

@@

It is clear that the artifact, as provided, is not in a suitable form
for preservation.  While it might be technically possible to automatically
capture the entire virtual machine and all of the connected filesystems,
it would require 166.8TB of storage, which would be prohibitively expensive
for capturing this one application alone.  Further, if multiple
similar applications are preserved, we would miss the opportunity to identify
common dependencies and store them once for multiple artifacts.
A more structured approach to dependency management is needed.

@@

Parrot is a virtual filesystem access tool which has been used to attach
existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
interface, and then replacing them with the desired I/O operations.  Parrot is already used
in the high energy physics community with applications like TauRoast specifically to 
provide access to the CMSSW software distribution via the CVMFS distributed file system.
We made small modifications to Parrot to record a \emph{namelist} which lists all 
of the files that an application actually accesses.

@@

For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
With duplicate filenames removed, the list is reduced to 67,168 files.
Many of those entries do not exist, because they reflect attempts
by the application to search for programs and libraries in multiple places.
Only 22,068 entries reflect existing files or directories.

@@

We evaluated the correctness of the reduced package and the overhead of generating the package.
To do this, the application was repeated with the help of \emph{Original Script} (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
Then one \emph{reduced package} was generated and verified with the help of Parrot on the original machine.

@@

We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
Then based on the successful execution of Original Script, we evaluated Reduced Package - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.

To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset. We also counted the time used to obtain the namelist and to generate the package. To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced Package.
Original Script does not support mining of implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Original Script and Reduced Package.
Reduced Package is faster than Original Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
and all the environment building only takes 4 seconds,
We were surprised that Reduced Package even reduces the actual analysis time. 
The reason for this is that data is obtained through accessing HDFS in Original Script, but is copied into the package in Reduced Package. This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Original& \bf Reduced\\ 
    \bf Category & \bf Script & \bf Package\\ \hline
    Obtain Namelist & N/A & 28min 28s \\ \hline
    Generate Package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 4s \\ \hline
    Analysis Code & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Original Script and Reduced Package}
    \label{table:time-2nd3rd}
\end{table}

Table~\ref{table:time-2nd3rd} also illustrates the time used to
obtain the namelist and to generate the package. 
The time used for these two steps is longer than the execution time,
because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
However, 
this is only done once.
Once the package is
generated, many users can directly obtain the package and repeat the application 
separately.

Table~\ref{table:size-original-real} on page 2 illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
The third column corresponds to the data size of Reduced Package and can be easily figured out, because all the necessary data has been copied into the package.
Original Script does not support measuring implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

To further verify the correctness of Reduced Package on other machines, two different machines are employed -
one virtual
machine~\cite{goldberg1974survey} from the Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
and one virtual machine from  the Amazon EC2~\cite{amazon2010amazon} Platform based on Xen.

Table~\ref{table:config-vm} illustrates the configuration of 
each machine and the execution time of the application on each machine.
All the machines adopt the x86\_64 hardware platform and Linux kernel.
Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
The execution time on one machine greatly depends on its hardware configuration.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|r|}
    \hline
    \bf Machine & \bf Distro & \bf CPU & \bf Mem & \bf Execution\\ 
    \bf Type   &\bf Version&\bf Cores & (\bf GB) & \bf Time\\ \hline
    Original &  Red Hat  & 64 & 125 & 13min 04s\\  
    Machine& 5.10 &&&\\ \hline
    KVM & CentOS & 4 & 2 & 21min 38s\\
    (Notre Dame)&5.10 &&&\\ \hline
    Xen & Red Hat & 16 & 60.5 & 13min 30s\\ 
    (EC2) &5.9 &&&\\ \hline
    \end{tabular}
    \caption{Evaluation of Different Machines}
    \label{table:config-vm}
\end{table}

In summary, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS kernel version.
%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.

@@

Generally, there are three approaches to preserve software environment:
hardware preservation, migration and emulation.  Hardware
preservation preserves the original software and its original operating
environment. 
Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
However, migration often involves the re-compiling and re-configuring
the source code to accommodate a new hardware platform and software environment.
Emulation recreates the original software and hardware environment by
programming future platforms and OSs. One common solution to implement this is
virtual machine. According to the usage and emulation degree of the real
machine, virtual machine can be divided into system virtual machine and process
virtual machine. 
The working principle, design principle and
performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
The
functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
scientific simulations in Java. 
The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.

@@

Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing a preserved software library have been made. 
The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
J. R. Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.

@@

B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.

@@

This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
OCI-1148330 (SI2) and PHY-1312842.
The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
\bibliographystyle{abbrv}
\bibliography{cclpapers,this}
